### 2024-07-19 conteudo/introduction/intro.tex
Try to change multiple-method as the whole methodology

\textbf{RQ1:} How effective is our approach in identifying and mitigating duplicate code in the Linux kernel?

@@

This research is divided into two phases. In \textbf{Phase I}, we will propose, build, and validate a tool capable 
of identifying code duplications at the function level for the C programming language. We expect this proposed tool 
to identify code duplications in the Linux kernel, as in our preliminary investigation of the code files in the kernel 
is commonly a union of duplicated and nonduplicated functions. To validate the tool, we will do a triangulation of results 
by evaluating our tool in the code duplication databases used in the formal literature and doing an empirical analysis 
in a set of randomly selected codes of the AMD Display driver which our proposed tool claims is a duplication. 
A detailed explication of how we will validate our tool is demonstrated in Chapter \ref{cha:method}.

@@

>>>>

\textbf{RQ1:} How effective is our approach in mitigating duplicate code in the Linux kernel?

@@

To address our research question, we do a multiple-method research utilizing different methodologies throughout 
the study. We structured this work into two phases, each with distinct research methods.

In \textbf{Phase I}, we will propose, build, and validate a tool capable 
of identifying code duplications at the function level for the C programming language. We expect this proposed tool 
to identify code duplications in the Linux kernel, as in our preliminary investigation of the code files in the kernel 
is commonly a union of duplicated and nonduplicated functions. To validate the tool, we will do a triangulation of results 
by evaluating our tool in the code duplication databases used in the formal literature and doing an empirical analysis 
in a set of randomly selected codes of the AMD Display driver which our proposed tool claims is a duplication. 
A detailed explication of how we will validate our tool is demonstrated in Chapter \ref{cha:method}.

@@

Figure (CREATE FIGURE AND ADD HERE) sumamarizes the research steps proposed in this work.
